---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# grainy

<!-- badges: start -->
<!-- badges: end -->

The goal of grainy is to encapsulate the logic of a raster grid in an object. 

## Installation

You can install the development version of grainy like so:

``` r
remotes::install_github("mdsumner/grainy")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(grainy)
g <- grain$new(c(360, 180), c(-180, 180, -90, 90))
g$cell_from_xy(cbind(0, 0))

## compare to raster/terra/stars/etc
#library(raster)
#cellFromXY(raster(extent(-180, 180, -90, 90), ncols = 360, nrows = 180), cbind(0, 0))
```

## Code of Conduct
  
Please note that the grainy project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
